Before going further into the calibration procedure, some initial definitions
have to be clarified:

\begin{itemize}

	\item {\bf WR Device}: any device that supports White Rabbit
		synchronization over an optical link. This can be e.g. the White Rabbit
		Switch, the SPEC board, or any custom hardware made for a specific
		application. A WR Device can run as WR Master or/and WR Slave.

	\item {\bf WR Calibrator}: any White Rabbit Device selected from the 
		available set that is used as a reference to calibrate the 
		rest of the White Rabbit Devices used in a synchronization system.

	\item {\bf WR Device TX latency} ($\Delta_{TX}$): WR PTP packet delay 
		from the moment it is timestamped in the transmission circuit
		inside the FPGA (WR Endpoint module) to the moment when the 
		transmitted packet reaches a fiber link. It is the sum of: 
		transmission delay inside FPGA chip; propagation delay of 
		electronic components and PCB traces; SFP transmitter delay.

	\item {\bf WR Device RX latency} ($\Delta_{RX}$): WR PTP packet delay 
		from the moment it reaches the receiving SFP module, to the 
		moment it is timestamped in the reception circuit inside the FPGA (WR
		Endpoint module). It is the sum of: SFP receiver delay; 
		propagation delay of electronic components and PCB traces; 
		reception delay inside FPGA chip.

	\item {\bf WR Device asymmetry} (2$\beta$): the difference between the TX 
		latency $\Delta_{TX}$ and the RX latency $\Delta_{RX}$.

	\item {\bf Fiber round-trip latency} ($\delta$): the total round-trip 
		delay of a fiber link (without the Tx/Rx latencies of the WR Devices). 
		It is the sum of the one-way propagation delays: Master-to-Slave 
		($\delta_{MS}$) and Slave-to-Master ($\delta_{SM}$).

	\item {\bf Relative delay coefficient} ($\alpha$): the parameter describing 
		the asymmetry (the difference between $\delta_{MS}$ and 
		$\delta_{SM}$) of the fiber used in a White Rabbit network. It 
		is the relative difference of Master-to-Slave and Slave-to-Master 
		propagation delays ($\alpha = \frac{\delta_{MS} - \delta_{SM}}
		{\delta_{SM}}$).

	\item {\bf Round trip delay} ($delay_{MM}$): the total packet delay on 
		a White Rabbit link. It is the sum of communicating parties (Master and
		Slave) fixed delays ($\Delta_{TXM}$, $\Delta_{RXM}$, $\Delta_{TXS}$,
		$\Delta_{RXS}$), bitslide values ($\epsilon_M$,
    $\epsilon_S$) and fiber round-trip latency ($\delta$).

\end{itemize}
