
\begin{thebibliography}{9}

\bibitem{IEEE1588}
  IEEE Std 1588-2008
  \emph{IEEE Standard for a Precision Clock Synchronization Protocol for
Networked Measurement and Control Systems}.
  IEEE Instrumentation and Measurement Society, New York,
  2008,
  http://ieee1588.nist.gov/.

\bibitem{IEEE8021D}
  IEEE Std 802.1D-2004
  \emph{IEEE Standard for Local and metropolitan area networks, Virtual Bridged
Local Area Networks}.
  LAN/MAN Standards Committee, New York,
  2006.

\bibitem{IEEE8021Q}
  IEEE Std 802.1Q-2005
  \emph{IEEE Standard for Local and metropolitan area networks Media Access
  Control (MAC) Bridges}.
  IEEE Computer Society, New York,
  2004.

\bibitem{IEEE8023}
  IEEE Std 802.3-2008
  \emph{IEEE Standard for Information technology - Telecommunications and
information exchange between systems - Local and metropolitan area networks -
Specific requirements}.
  IEEE Computer Society, New York,
  2008.

\bibitem{UplinkFast}
  CISCO Document ID: 10575
  \emph{Understanding and Configuring the Cisco UplinkFast Feature}.
  http://www.cisco.com.

\bibitem{SynchE}
  ITU-T G.8262/Y.1362
  \emph{Timing characteristics of a synchronous
  Ethernet equipment slave clock}.
  TELECOMMUNICATION STANDARDIZATION SECTOR OF ITU, 
  07/2010.

\bibitem{WRPTP}
 Emilio G. Cota, Maciej Lipinski, Tomasz Wostowski, Erik van der Bij, Javier
 Serrano
  \emph{White Rabbit Specification: Draft for Comments}.
  CERN, Geneva
  09/2010.

\bibitem{FAIR}
  R.Bar
   \emph{The FAIR Accelerator Control System}
   The excerpt from the updated FAIR Technical Design Report,
   Hamburg,
   2008.
   
\bibitem{DesigningLSLANs}
  Kevin Dooley
  \emph{Designing Large-Scale LANs}
  O'REILLY,
  2002.

\bibitem{HWpresentation}
  Tomasz Wlostowski
  \emph{White Rabbit HW status}
  White Rabbit Developers Meeting, Geneva, CERN
  December 2010,
  http://www.ohwr.org/attachments/404/hw\_pres.odp

\bibitem{PropagationDelay}
  P.P.M. Jansweijer,
  H.Z. Peek
  \emph{Measuring propagation delay over a 1.25 Gbps
         bidirectional data link}
  National Institute for Subatomic Physics, Amsterdam
  May 31, 2010.

\bibitem{FAIRtiming}
   T. Fleck 
   R. Bar 
  \emph{FAIR Accelerator Control System 
        Baseline Technical Report }
  DRAFT,
  Hamburg,
  2009.

\bibitem{CERNtiming}
  Mr. XXX
  \emph{I need some nice doc here :) }
  Current source: Javier + Julian,
  CERN, Geneva,
  xxx.

\bibitem{ciscoRSTP}
  Mr. XXX
  \emph{I read the doc, I cannot find it at the moment }
  CISCO,
  somewhere,
  xxxx.

\bibitem{FAIRtimingSystem}
  T. Fleck, C.Prados, S.Rauch, M.Kreider
  \emph{FAIR Timing System}
  GSI,
  v1.2,
  12.05.2009.

\bibitem{The All-New Switch Book: The Complete Guide to LAN Switching Technology}
 Rich Seifert, James Edwards
 \emph{The All-New Switch Book: The Complete Guide to LAN Switching Technology}
 Wiley Pusblishing, Inc. 

\bibitem{IEEE8021Qbb} 
 \emph{IEEE 802.1Qbb/D2.3. Draft Standard for Local and Metropolitan Area
      Networks - Virtual Bridged Local Area Networks - Amendment XX:
Priority-based Flow Control.}  
   June 9,
  2009.

\bibitem{atm_traffic} 
 \emph{Network Testing Solutions, ATM Traffic Management White paper}

\bibitem{FlowControllers} 
 \emph{... missing citation...}

\bibitem{reed_solomon} 
 \emph{RFC 5510 Reed-Solomon Forward Error Correction (FEC) Schemes}
J. Peltotalo
S. Peltotalo
Tampere University of Technology
April 2009

\bibitem{reed_solomon_theory}
\emph{An Introduction to Galois Fields and Reed-Solomon Coding}
James Westall
James Martin
School of Computing
Clemson University
October 4, 2010

\bibitem{hamming_Codes}
\emph{Hamming Codes}
Charles B. Cameron
Electrical Engineering Department, 
United States Naval Academy
Department of Electrical Engineering .
April 19, 2005

\bibitem{TomekMSc} 
 \emph{Precise time and frequency transfer in a White Rabbit netwokr, MSc
Thesis}
  Tomasz Wlostowski
  Warsaw University of Technology
  To be published.

\bibitem{WRdemo} 
 \emph{White Rabbit DEMO(2)}
  Tomasz Wlostowski,
  Maciej Lipinski
  CERN, Geneva,
  11/2010.

\bibitem{FaultTree} 
 \emph{Reliability Workbench, FaultTree}
  www.Isograph.com.

\end{thebibliography}
